Frugivoria frugivore trait subset

### 2024-06-10 code/L1/L1_F2_TropicalAndes_frugivore_traits.Rmd
add code to visualize trait record completeness

---
title: "Frugivoria frugivore trait subset"
author: "Hazel J. Anderson"
project: "Plant-Frugivore Diversity"
collaborators: "Beth E. Gerstner, Phoebe L. Zarnetske"
overview: "Subsetting Frugivoria to the species and traits of interest"
data input: "TropicalAndes_Frugivoria_frugivore_traits.csv", "TropicalAndes_GBIF_frugivore_occ_cleaned.csv"
data output: "TropicalAndes_Frugivoria_traits_subset.csv"
date: "2023-10-31"
output: html_document
---

# Load required packages
```{r}
library(dplyr)
```

@@

```{r}
source("~/GitHub/neotropical_plants/code/L0/data_summary.R")
```

@@

@@

>>>>

---
title: "Frugivoria frugivore trait subset"
author: "Hazel J. Anderson"
project: "Plant-Frugivore Diversity"
collaborators: "Beth E. Gerstner, Phoebe L. Zarnetske"
overview: "Subsetting Frugivoria to the species and traits of interest."
data input: "TropicalAndes_Frugivoria_frugivore_traits.csv, TropicalAndes_GBIF_frugivore_occ_cleaned.csv"
data output: "TropicalAndes_Frugivoria_traits_subset.csv"
date: "2023-10-31"
output: 
  html_document:
    code-link: true
---

# Load required packages
```{r}
library(dplyr)
library(funbiogeo)
library(visdat)
```

@@

```{r}
source("~/GitHub/neotropical_plants/code/data_summary.R")
```

@@

```{r}
fb_plot_species_traits_completeness(Frugivoria_subset)
fb_plot_number_species_by_trait(Frugivoria_subset)
fb_table_trait_summary(Frugivoria_subset)
```

```{r}
vis_dat(Frugivoria_subset)
vis_miss(Frugivoria_subset)
```

@@

# Package citations and session info
```{r}
library(report)
report::cite_packages()

devtools::session_info()
```
